---
title: "flat_additional.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

## `extract_html_slides()` : extract html each elements of slides from multiple html files

```{r function-extract_html_slides}
#' Extract html slide content
#'
#' Extract slide content from multiple html
#'
#' @param vec_html_path character. The vector of path to individual html files
#'
#' @importFrom tools file_ext
#' @importFrom rvest read_html html_elements html_children
#' @importFrom htmltools HTML
#'
#' @return HTML. The HTML slide content of all html files combined together.
#'
#' @export
extract_html_slides <- function(
    vec_html_path
  ) {
  # verify path are html files
  not_all_files_are_html <- any(
    file_ext(vec_html_path) != "html"
  )
  if (isTRUE(not_all_files_are_html)) {
    stop("Some of the input files are not html files.")
  }
  
  # extract all slides elements
  list_html_slides <- lapply(
    X = vec_html_path,
    FUN = \(html_path) {
      html_path |>
        read_html() |>
        html_elements(".slides") |>
        html_children() |>
        as.character()
    }
  )
  
  # edit content for proper slide formating
  list_html_slides <- lapply(
    X = seq_along(list_html_slides),
    FUN = \(slide_number) {
      list_html_slides[[slide_number]] |>
        # rename 1st slide to avoid duplicated title-slide ids
        gsub(
          pattern = "title-slide",
          replacement = paste0("title-slide-", as.character(slide_number))
        )
    }
  )
  
  # compile all slides content into a single HTML text
  html_content <- list_html_slides |>
    unlist() |>
    paste0(collapse = "\n") |> 
    HTML()
  
  return(html_content)
}
```

```{r example-extract_html_slides}
# list html files
courses_path <- system.file(
  "courses",
  package = "squash"
)

htmls <- list.files(
  path = courses_path,
  full.names = TRUE,
  recursive = TRUE,
  pattern = "html$"
)

html_slide_content <- extract_html_slides(vec_html_path = htmls)
```

```{r tests-extract_html_slides}
# create temp dir
temp_dir <- tempfile(pattern = "template")
dir.create(temp_dir)

# copy qmd in tmp
squash_path <- system.file(package = "squash")

files_to_copy <- c(
  file.path(
    squash_path,
    c("_extensions",
      "courses",
      "_quarto.yaml",
      "_quarto-render.yml")
  )
)

file.copy(
  from = files_to_copy,
  to = temp_dir,
  recursive = TRUE
)

# render all course qmd in quarto project with default profile
# remove as_job to not run as background jobs
quarto::quarto_render(
  input = temp_dir,
  as_job = FALSE
)

# list created html
htmls <- list.files(
  path = temp_dir,
  pattern = "qmd[0-9]_for_test\\.html$",
  recursive = TRUE,
  full.names = TRUE
)
  
test_that("extract_html_slides returns all html slide classes in correct order", {
    
  # run function with slide order 1-2-3
  html_slide_content <- extract_html_slides(
    vec_html_path = htmls
    )
  
  #' @description test with three html files in order 1-2-3
  expect_snapshot(x = html_slide_content)
  
  # run function with slide order 2-1-3
  html_slide_content_reordered <- extract_html_slides(vec_html_path = htmls[c(2, 1, 3)])
  
  #' @description test with three htmls in order 2-1-3
  expect_snapshot(x = html_slide_content_reordered)

})

# clean up
unlink(temp_dir, recursive = TRUE)
```

## `create_template_html()` : create a template html with ThinkR styling

Use the quakr extension to render html.

```{r function-create_template_html}
#' Create a themed html from a qmd template
#' 
#' Create a template html with ThinkR styling
#' 
#' @param path_to_qmd character. Path to the qmd template to be rendered in thinkridentity-revealjs
#' @param output_file character. Name of the output html template
#' @param temp_dir character. Path to the temp_dir where template will be rendered
#' 
#' @inheritParams compile_qmd_course
#' 
#' @importFrom quarto quarto_render
#' @importFrom utils download.file unzip
#' @importFrom yaml write_yaml
#'
#' @return character. Path to the html template
#' 
#' @export
create_template_html <- function(
  path_to_qmd,
  output_file,
  output_dir,
  title = "Formation R",
  date = '01/01/01-01/01/01',
  temp_dir = tempfile(pattern = "template")
  ){
    
  # set qmd file name base on html output name
  output_file_qmd <- gsub("\\.html", "\\.qmd", output_file)
  
  # copy qmd template to temp_dir with new name
  if (!file.exists(temp_dir)){
    dir.create(temp_dir)
  }
  
  file.copy(
    from = path_to_qmd,
    to = file.path(
      temp_dir,
      output_file_qmd)
    )
  
  # copy quakr _extensions from {squash} inst
  dir.create(file.path(temp_dir, "_extensions/"))
  
  file.copy(
    from = system.file(
      "_extensions",
      package = "squash"
    ),
    to = temp_dir,
    recursive = TRUE
  )
  
  # define quarto project parameters
  write_yaml(
    x = list(
      "title" = title,
      "subtitle" = date,
      "format" = "thinkridentity-revealjs"
      ),
    file = file.path(temp_dir, "_quarto.yml")
  )
  
  # render template with parameters of quarto project
  quarto_render(
    input = file.path(temp_dir, output_file_qmd),
    quiet = TRUE)
  
  # copy output html and companion folders to output_dir
  files_to_copy <- c(
    "html" = file.path(temp_dir, output_file),
    "lib_folder" = file.path(temp_dir, gsub("\\.html", "_files", output_file)),
    "ext_folder" = file.path(temp_dir, "_extensions")
  )
  
  if (!file.exists(output_dir)){
    dir.create(output_dir)
  }
  
  file.copy(
    from = files_to_copy,
    to = output_dir,
    recursive = TRUE
  )
  
  # remove temp_dir
  unlink(temp_dir, recursive = TRUE)
  
  # return path to html template
  return(file.path(output_dir, output_file))
}
```
  
```{r example-create_template_html}
# create temp dir
temp_dir <- tempfile(pattern = "template")

# create html template
path_to_html_template <- create_template_html(
  path_to_qmd = system.file("template.qmd", package = "squash"),
  output_dir = temp_dir,
  output_file = "complete_course.html"
)

# clean up
unlink(temp_dir, recursive = TRUE)
```
  
```{r tests-create_template_html}
# create temp dir
temp_dir <- tempfile(pattern = "template")

test_that("create_template_html generate an html with proper title and theme", {

  # create html template
  path_to_html_template <- create_template_html(
    path_to_qmd = system.file("template.qmd", package = "squash"),
    output_dir = temp_dir,
    output_file = "complete_course.html"
  )
  
  # list files in extensions
  expect_extension_files <- list.files(
    file.path(temp_dir, "_extensions"),
    recursive = TRUE
  )
  
  # extract html content
  slide_content <- path_to_html_template |>
    read_html() |>
    html_elements(css = ".slides") |>
    html_children() |>
    as.character()
  
  #' @description test quakr extension dir is correctly copied
  expect_setequal(
    object = expect_extension_files,
    expected = c(
      "ThinkR-open/thinkridentity/_extension.yml",
      "ThinkR-open/thinkridentity/background.png",
      "ThinkR-open/thinkridentity/logo.png",
      "ThinkR-open/thinkridentity/logo.svg",
      "ThinkR-open/thinkridentity/thinkridentity.scss"
    )
  )
  
  #' @description test html content of template has correct theme and title
  expect_snapshot(x = slide_content)
  
})

# clean up
unlink(temp_dir, recursive = TRUE)
```


## `clean_rendering_files()` : cleanup course directory after rendering

Utility function to remove all the files and folders created when rendering a qmd. The files already present and updated will not be removed.
    
```{r function-clean_rendering_files}
#' Clean folder after quarto rendering
#' 
#' Remove all the files and folders created when rendering a qmd to html
#' 
#' @param dir character. The directory to look for rendering output recursively.
#' @param present_before character. Path to the files and directories present before rendering.
#' 
#' @return None. Side effect: remove files that were not present before rendering
#' 
#' @export
clean_rendering_files <- function(
    dir,
    present_before
){
    
  # list files
  present_after <- unique(
    list.files(
      path = dir,
      full.names = TRUE,
      recursive = TRUE,
      include.dirs = TRUE
    )
  )
  
  file_created_by_rendering <- setdiff(
    x = present_after,
    y = path.expand(present_before)
  )
  
  unlink(
    x = file_created_by_rendering,
    recursive = TRUE
  )
  
}
```
  
```{r example-clean_rendering_files}
# create a temp dir with qmd
temp_dir <- tempfile(pattern = "clean")

dir.create(
  path = file.path(temp_dir, "img"),
  recursive = TRUE
)

file.copy(
  from = system.file("courses", "C01", "qmd1_for_test.qmd", package = "squash"),
  to = temp_dir
)

file.copy(
  from = system.file("courses", "C01", "img", "logo_1.png", package = "squash"),
  to = file.path(temp_dir, "img")
)

# list files before rendering
file_and_dirs_before <- list.files(
  temp_dir,
  recursive = TRUE,
  full.names = TRUE,
  include.dirs = TRUE
)

# render qmd
quarto::quarto_render(
  input = file.path(temp_dir, "qmd1_for_test.qmd"),
  quiet = TRUE
)

# remove created files and dirs
clean_rendering_files(
  dir = temp_dir,
  present_before = file_and_dirs_before
)

# clean temp dir
unlink(temp_dir, recursive = TRUE)
```
  
```{r tests-clean_rendering_files}
# create a temp dir with qmd
temp_dir <- tempfile(pattern = "clean")

dir.create(
  path = file.path(temp_dir, "img"),
  recursive = TRUE
)

file.copy(
  from = system.file("courses", "C01", "qmd1_for_test.qmd", package = "squash"),
  to = temp_dir
)

file.copy(
  from = system.file("courses", "C01", "img", "logo_1.png", package = "squash"),
  to = file.path(temp_dir, "img")
)

# list files before rendering
file_and_dirs_before <- list.files(
  temp_dir,
  recursive = TRUE,
  full.names = TRUE,
  include.dirs = TRUE
)

# render qmd
quarto::quarto_render(
  input = file.path(temp_dir, "qmd1_for_test.qmd"),
  quiet = TRUE
)

test_that("clean_rendering_files removes all the file that are generated by quarto rendering", {
  
  # remove created files and dirs
  clean_rendering_files(
    dir = temp_dir,
    present_before = file_and_dirs_before
  )
  
  # list files after rendering
  file_present_now <- list.files(
    temp_dir,
    recursive = TRUE,
    full.names = TRUE,
    include.dirs = TRUE
  )
  
  #' @description test list of files is the same before and after
  expect_setequal(
    object = file_present_now,
    expected = file_and_dirs_before)
  
})

# clean temp dir
unlink(temp_dir, recursive = TRUE)
```

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_utils.Rmd",
  vignette_name = NA,
  check = FALSE
  )
```

