---
title: "Using parallel workers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using parallel workers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval=FALSE, echo=FALSE}
# list example qmds
courses_path <- system.file(
  "courses",
  "M01",
  package = "squash"
)

# copy course tree in tmpdir, add quarto porject file
tmp_course_path <- tempfile(pattern = "course")
dir.create(tmp_course_path)
file.create(file.path(tmp_course_path, "_quarto.yaml"))

file.copy(
  from = courses_path,
  to = tmp_course_path,
  recursive = TRUE
)

qmds <- list.files(
  path = tmp_course_path,
  full.names = TRUE,
  recursive = TRUE,
  pattern = "qmd$"
)

# generate html in temp folder
temp_dir <- tempfile(pattern = "compile")
```

Inside `{squash}`, the individual rendering of quarto presentation files is managed via `{future}` and `{furrr}` packages, meaning you can parallelize the generation of several chapters at once.

To do so, you need to setup the `future::plan()` with your selected behavior (e.g. `sequential` or `multisession`) before running the compilation.

```{r, eval=FALSE}
library(squash)

# set parallel rendering with future
future::plan(future::multisession, workers = 2)

html_output <- compile_qmd_course(
  vec_qmd_path = qmds,
  output_dir = temp_dir,
  output_html = "complete_course.html"
)

# reset default future plan
future::plan("default")
```

By running the above command, `{squash}` will first warn you that a non-default plan is detected for running the compilation. It will then proceed to render the html.

```{r, echo=FALSE}
cli::cli_alert_info("{{future}} is using plan(multisession, workers = 2), to modify this use `future::plan()`")
cli::cli_alert_success("All qmd rendered.")
```


## A note on future

* Future plan will not be modified by `{squash}`, you may want to restor default plan after rendering with the `future::plan("default")` command.

* Parallel rendering in currently not natively supported by quarto. As a result, please use parallel rendering at your own risk, as it is likely to become unstable with an increasing number of quarto chapter files.

* Unstability is likely caused by temporary execution directories that may be erased by a sub-process while still being looked for in another subprocess.

```{r, eval=FALSE, echo=FALSE}
# clean up
unlink(temp_dir, recursive = TRUE)
unlink(tmp_course_path, recursive = TRUE)
```
