---
title: "Using parallel workers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using parallel workers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval=FALSE}
#| include: false

# list example qmds
courses_path <- system.file(
  "courses",
  "M01",
  package = "squash"
)

# copy course tree in tmpdir, add quarto porject file
tmp_course_path <- tempfile(pattern = "course")
dir.create(tmp_course_path)
file.create(file.path(tmp_course_path, "_quarto.yaml"))

file.copy(
  from = courses_path,
  to = tmp_course_path,
  recursive = TRUE
)

qmds <- list.files(
  path = tmp_course_path,
  full.names = TRUE,
  recursive = TRUE,
  pattern = "qmd$"
)

# generate html in temp folder
temp_dir <- tempfile(pattern = "compile")

```

The individual rendering of qmd files is managed with the `{future}` and `{furrr}` packages, meaning you can parallelize the generation of several chapters at once.

To do so, you need to setup the future `plan()` with your selected behavior (e.g. `sequential` or `multisession`) before running the compilation.

```{r, eval=FALSE}
library(future)

# set parallel rendering with future
plan(multisession, workers = 2)

html_output <- compile_qmd_course(
  vec_qmd_path = qmds,
  output_dir = temp_dir,
  output_html = "complete_course.html"
)

# reset default future plan
plan("default")
```

## A note on future

Parallel rendering in currently not natively supported by quarto. As a result, please use parallel rendering at your own risk, as it is likely to become unstable with an increasing number of qmd chapter files.

This is caused by temporary execution directories that may be erased by a sub-process while still being looked for in another subprocess.

```{r, eval=FALSE}
# clean up
unlink(temp_dir, recursive = TRUE)
unlink(tmp_course_path, recursive = TRUE)
```

