---
title: "Using personnalised template"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using personnalised template}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval=FALSE}
#| include: false

# list example qmds
courses_path <- system.file(
  "courses",
  "M01",
  package = "squash"
)

# copy course tree in tmpdir, add quarto porject file
tmp_course_path <- tempfile(pattern = "course")
dir.create(tmp_course_path)
file.create(file.path(tmp_course_path, "_quarto.yaml"))

file.copy(
  from = courses_path,
  to = tmp_course_path,
  recursive = TRUE
)

qmds <- list.files(
  path = tmp_course_path,
  full.names = TRUE,
  recursive = TRUE,
  pattern = "qmd$"
)

# generate html in temp folder
temp_dir <- tempfile(pattern = "compile")

```

By default, `{squash}` will include your qmd chapters into a minimal template with no extra slide then the title one.

You can provide a personalized template, and include some custom placeholder as necessary.

The only requirement for your template is to keep the `{{ include_html_content }}` placeholder, as it will be the landing spot for including the chapter slides.

Let's use the following template :

```{.md}

{{ include_html_content }}

---


## {{ trainer }}

**{{ phone }}**

**{{ mail }}**
```

> This template is available via `system.file("template.qmd", package = "squash")`

In this template, I add three new placeholders in a last slide to mention a trainer's contact details.

I can now render my template with customized info in these new slots with the following command :

```{r, eval=FALSE}
library(squash)

html_output <- compile_qmd_course(
  vec_qmd_path = qmds,
  output_dir = temp_dir,
  output_html = "complete_course.html",
  template = system.file("template.qmd", package = "squash"),
  template_text = list(
    "trainer" = "Rudolph",
    "phone" = "36 15 36 15",
    "mail" = "alloperenoel.com"
  )
)
```

You can add as many new placeholder as you wish, as long as you provide it with a value in the `template_text` input list.

You can also add some fixed content directly into the template that will be rendered without the need of extra parameters.

```{r, eval=FALSE}
# clean up
unlink(temp_dir, recursive = TRUE)
unlink(tmp_course_path, recursive = TRUE)
```
