---
title: "Using quarto extensions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using quarto extensions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval=FALSE}
# list example qmds
courses_path <- system.file(
  "courses",
  "M01",
  package = "squash"
)

# copy course tree in tmpdir, add quarto porject file
tmp_course_path <- tempfile(pattern = "course")
dir.create(tmp_course_path)
file.create(file.path(tmp_course_path, "_quarto.yaml"))

file.copy(
  from = courses_path,
  to = tmp_course_path,
  recursive = TRUE
)

qmds <- list.files(
  path = tmp_course_path,
  full.names = TRUE,
  recursive = TRUE,
  pattern = "qmd$"
)

# generate html in temp folder
temp_dir <- tempfile(pattern = "compile")

```

## Using quarto themes

Let's say the default quarto theme is somewhat not your style, how could you include your preferred quarto theme ?

To do so, you first need to install this extension on your machine like you would do for a single qmd file rendering.

```{.bash}
quarto add ArthurData/quarto-revealjs-lilleuniv
```

Great, now you can use this theme with `{squash}` by providing the target theme as `output_format` and the `_extensions` folder path as `ext_dir`.

```{r, eval=FALSE}
html_output <- compile_qmd_course(
  vec_qmd_path = qmds,
  output_dir = temp_dir,
  output_html = "complete_course.html",
  output_format = "revealjs-lille-univ-dark-revealjs",
  ext_dir = "path/to/_extensions"
)
```

## Using quarto plugins

Cool right ? But let's go further and add a plugin in the `_extensions` folders !

```{.bash}
quarto add ArthurData/quarto-confetti
```

I can now add this plugin in the rendering metadata to integrate it in my presentation.

```{r, eval=FALSE}
html_output <- compile_qmd_course(
  vec_qmd_path = qmds,
  output_dir = temp_dir,
  output_html = "complete_course.html",
  metadata_template = list(
    `revealjs-plugins` = c("confetti")
  ),
  ext_dir = "path/to/_extensions"
)
```

## A note on extensions

In order to use themes and plugins, you can only provide a single `_extensions` folder via the `ext_dir` parameter, so make sure all the necessary folders are installed in there.

You can edit the metadata a the template level (`metadata_template` input) and/or the qmd level (`metadata_qmd` input). It is usually best for plugins and themes to be applied at the template level (which will be source of the main html output file).

When rendering a qmd file, `{squash}` will make sure the qmd can access the provided `_extensions` folder. Two scenarios can be triggered :

- the qmd is part of a quarto project : the `_extensions` folder is copied in the quarto project root and cleaned after rendering
- the qmd is **not** part of a quarto project : the `_extensions` folder is copied in the qmd folder and cleaned after rendering

In both cases, if the extensions are already present in the target location, a note will be raised in the console and `{squash}` will use the existing extensions without overriting.

```{r, eval=FALSE}
# clean up
unlink(temp_dir, recursive = TRUE)
unlink(tmp_course_path, recursive = TRUE)
```
