---
title: "Advanced usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
#| include: false

# list example qmds
courses_path <- system.file(
  "courses",
  "M01",
  package = "squash"
)

# copy course tree in tmpdir, add quarto porject file
tmp_course_path <- tempfile(pattern = "course")
dir.create(tmp_course_path)
file.create(file.path(tmp_course_path, "_quarto.yaml"))

file.copy(
  from = courses_path,
  to = tmp_course_path,
  recursive = TRUE
)

qmds <- list.files(
  path = tmp_course_path,
  full.names = TRUE,
  recursive = TRUE,
  pattern = "qmd$"
)

# generate html in temp folder
temp_dir <- tempfile(pattern = "compile")

```

## Using personnalised template

By default, `{squash}` will include your qmd chapters into a minimal template with no extra slide then the title one.

You can provide a personalized template, and include some custom placeholder as necessary.

The only requirement for your template is to keep the `{{ include_html_content }}` placeholder, as it will be the landing spot for including the chapter slides.

Let's use the following template :

```{.md}

{{ include_html_content }}

---


## {{ trainer }}

**{{ phone }}**

**{{ mail }}**
```

> This template is available via `system.file("template.qmd", package = "squash")`

In this template, I add three new placeholders in a last slide to mention a trainer's contact details.

I can now render my template with customized info in these new slots with the following command :

```{r, eval=FALSE}
library(squash)

html_output <- compile_qmd_course(
  vec_qmd_path = qmds,
  output_dir = temp_dir,
  output_html = "complete_course.html",
  template = system.file("template.qmd", package = "squash"),
  template_text = list(
    "trainer" = "Rudolph",
    "phone" = "36 15 36 15",
    "mail" = "alloperenoel.com"
  )
)
```

You can add as many new placeholder as you wish, as long as you provide it with a value in the `template_text` input list.

You can also add some fixed content directly into the template that will be rendered without the need of extra parameters.

## Using quarto extensions (theme and plugin)

Let's now say the default quarto theme is somewhat not your style, how could you include your preferred quarto theme ?

To do so, you first need to install this extension on your machine like you would do for a single qmd file rendering.

```{.bash}
quarto add ArthurData/quarto-revealjs-lilleuniv
```

Great, now you can use this theme with `{squash}` by providing the target theme as `output_format` and the `_extensions` folder path as `ext_dir`.

```{r, eval=FALSE}
html_output <- compile_qmd_course(
  vec_qmd_path = qmds,
  output_dir = temp_dir,
  output_html = "complete_course.html",
  output_format = "revealjs-lille-univ-dark-revealjs",
  ext_dir = "path/to/_extensions"
)
```

Cool right ? But let's go further and add a plugin in the `_extensions` folders !

```{.bash}
quarto add ArthurData/quarto-confetti
```

I can now add this plugin in the rendering metadata to integrate it in my presentation.

```{r, eval=FALSE}
html_output <- compile_qmd_course(
  vec_qmd_path = qmds,
  output_dir = temp_dir,
  output_html = "complete_course.html",
  metadata_template = list(
    `revealjs-plugins` = c("confetti")
  ),
  ext_dir = "path/to/_extensions"
)
```

### A note on extensions

In order to use themes and plugins, you can only provide a single `_extensions` folder via the `ext_dir` parameter, so make sure all the necessary folders are installed in there.

You can edit the metadata a the template level (`metadata_template` input) and/or the qmd level (`metadata_qmd` input). It is usually best for plugins and themes to be applied at the template level (which will be source of the main html output file).

When rendering a qmd file, `{squash}` will make sure the qmd can access the provided `_extensions` folder. Two scenarios can be triggered :

- the qmd is part of a quarto project : the `_extensions` folder is copied in the quarto project root and cleaned after rendering
- the qmd is **not** part of a quarto project : the `_extensions` folder is copied in the qmd folder and cleaned after rendering

In both cases, if the extensions are already present in the target location, a note will be raised in the console and `{squash}` will use the existing extensions without overriting.

## Using parallel workers

The individual rendering of qmd files is managed with the `{future}` and `{furrr}` packages, meaning you can parallelize the generation of several chapters at once.

To do so, you need to setup the future `plan()` with your selected behavior (e.g. `sequential` or `multisession`) before running the compilation.

```{r, eval=FALSE}
library(future)

# set parallel rendering with future
plan(multisession, workers = 2)

html_output <- compile_qmd_course(
  vec_qmd_path = qmds,
  output_dir = temp_dir,
  output_html = "complete_course.html"
)

# reset default future plan
plan("default")
```

### A note on future

Parallel rendering in currently not natively supported by quarto. As a result, please use parallel rendering at your own risk, as it is likely to become unstable with an increasing number of qmd chapter files.

This is caused by temporary execution directories that may be erased by a sub-process while still being looked for in another subprocess.

```{r, eval=FALSE}
# clean up
unlink(temp_dir, recursive = TRUE)
unlink(tmp_course_path, recursive = TRUE)
```

