---
title: "Contributing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Contributing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`{squash}` is an open-source project, and we welcome contributions of all kinds.

## Contributing to {squash}

Development of {squash} happens on GitHub. You can contribute to the package in several ways:

- **Reporting issues**: If you find a bug, please file a minimal reproducible example on [GitHub](https://github.com/ThinkR-open/squash/issues) with a clear description of the issue.

- **Contributing code**: If you want to contribute code, please open a pull request on [GitHub](https://github.com/ThinkR-open/squash/pulls).

- **Documentation**: If you find a typo or error in the documentation, please open a pull request on [GitHub](https://github.com/ThinkR-open/squash/pulls).

- **Ideas**: If you have an idea for a new feature, please open an issue on [GitHub](https://github.com/ThinkR-open/squash/issues) to discuss it.

Any contribution is welcome!


## Note for the contributors

If you want to contribute to the package, please note that the package is structured as follows:

- The main functions are in the `R/` folder.

- The tests are in the `tests/` folder.

- The documentation is in the `man/` folder.

- The vignettes are in the `vignettes/` folder.

- The squash template files are in the `inst/` folder.

## Code style

This package follows the `grkstyle` style guide. Please make sure to follow the same style when contributing to the package.

## Actual state of the package

The package is in active development. The actual state of the check for `main` is:
[![R-CMD-check](https://github.com/ThinkR-open/squash/actions/workflows/R-CMD-check.yaml/badge.svg?branch=main)](https://github.com/ThinkR-open/squash/actions/workflows/R-CMD-check.yaml)

Please make sure that your contribution does not break the package. You can run the checks locally by running the following code:

```{r, eval=FALSE}
devtools::check()
```

You can run the following code to trigger interactive tests that ask for user validation of the output:

```{r, eval=FALSE}
devtools::test()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/1/0/0/code-of-conduct.html). 
By participating in this project you agree to abide by its terms.
