---
title: "Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

_What is `{squash}` made for?_

This package has been developed to enable the generation of a single html presentation file from multiple independent quarto files.

Given a list of qmd files, `{squash}` will individually render them with the specified metadata and combine their content into a single template file.

Relative references to image and external data in each single qmd file will be functional and embedded in the final html presentation.

## How do I use {squash} ?

This is a basic example of combining qmd files into a single html presentation.

Let's say we have two folders with qmd files inside, refering to some logo images.

```{r}
#| include: false

# list example qmds
courses_path <- system.file(
  "courses",
  "M01",
  package = "squash"
)

# copy course tree in tmpdir
tmp_course_path <- tempfile(pattern = "course")
dir.create(tmp_course_path)

file.copy(
  from = courses_path,
  to = tmp_course_path,
  recursive = TRUE
)
```

```{r}
fs::dir_tree(tmp_course_path)

qmds <- list.files(
  tmp_course_path,
  full.names = TRUE,
  recursive = TRUE,
  pattern = "qmd$"
)

qmds
```

I can render a single html presentation from these qmd by executing the following command :

```{r}
library(squash)

html_output <- compile_qmd_course(
  vec_qmd_path = qmds,
  output_dir = file.path(tmp_course_path, "complete"),
  output_html = "complete_course.html",
  quiet = TRUE
)
```

Tada, I now have a new folder, with my complete html presentation alongside the necessary external image files, stored in individual sub-folder to prevent overriding.

```{r}
fs::dir_tree(tmp_course_path, recurse = 2)
```

```{r}
#| include: false

unlink(tmp_course_path, recursive = TRUE)
```


## Remarks

* Files will be included in the same order provided to `compile_qmd_course`.

* Metadata and parameters set in the `compile_qmd_course` will supersede the parameters detected inside the qmd header and/or the quarto project metadata files.

* {squash} can work both inside and outside of a quarto project, qmd files to combine together can also come from different quarto projects.

* In case of failure to render some files, `{squash}` will erase all temporarily created files before exiting.
